---
title: "process-eBird-data"
author: "Sarah Supp"
date: "2/19/2021"
output: html_document
---

##Code for hummingbird migration project
(c) 2020, Supp, Graham, La Sorte, and Graham
supps@denison.edu
Denison University
Code is under development
Modified from code that is part of Eastern Redcedar project for NSF Multi-Institution Collaborative Award (2019-22) and modified fro previous code developed for Supp et al. 2015 hummingbird paper (Ecography)

Hummingbirds evaluated include: 
* Black-chinned _Archilochus alexandri_
* Ruby-throated _A. colubris_
* Calliope _Selasphorus calliope_
* Broad-tailed _S. playcercus_
* Rufous _S. rufus_

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
```

If starting from scratch, input the three raw data files and merge together.
You need to bring in: 
1. a file with the bird observations (ebrd2.c)
2. a file with the total eBirder "effort" (eft.c)
3. a file with all the center locations for the POLYFID grid cells (locs)

Load the eBird effort and location files, from FAL (July 2020)
```{r}
# raw eBirder data, queried by FAL
 load("data/raw_eBird_data/effort2020.Rdata") # will come in as eft.c, FAL named previously
 load("data/raw_eBird_data/locs_2020.Rdata") # will come in as locs, FAL named previously
```

For *A. alexandri*
```{r}
load("data/raw_eBird_data/Archilochus_alexandri.RData") # will come in as ebrd2.c, FAL named previously

# #merge locations data on POLYFID so it includes the center of each hex cell (LONGITUDE.y, LATITUDE.y)
  dat_merged = merge(ebrd2.c, locs, by.x = "POLYFID", by.y = "POLYFID")
  
  #now merge with the third data file for effort 
  #where count.x is number of target species and count.y is total number of eBird records (including those without the target species)
  dat_effort = merge(dat_merged, eft.c, by.x = c("POLYFID", "YEAR", "DAY"), by.y = c("POLYFID","YEAR",  "DAY")) 
  dat_effort$DAY <- as.numeric(dat_effort$DAY) 
  dat_effort$species <- "Archilochus alexandri"
  saveRDS(dat_effort, file = "data/dat_effort_bchu.rds")
```

For *A. colubris*
```{r}
load("data/raw_eBird_data/Archilochus_colubris.RData") # will come in as ebrd2.c, FAL named previously

# #merge locations data on POLYFID so it includes the center of each hex cell (LONGITUDE.y, LATITUDE.y)
  dat_merged = merge(ebrd2.c, locs, by.x = "POLYFID", by.y = "POLYFID")
  
  #now merge with the third data file for effort 
  #where count.x is number of target species and count.y is total number of eBird records (including those without the target species)
  dat_effort = merge(dat_merged, eft.c, by.x = c("POLYFID", "YEAR", "DAY"), by.y = c("POLYFID","YEAR",  "DAY")) 
  dat_effort$DAY <- as.numeric(dat_effort$DAY) 
  dat_effort$species <- "Archilochus colubris"
  saveRDS(dat_effort, file = "data/dat_effort_rthu.rds")
```

For *Selasphorus calliope*
```{r}
load("data/raw_eBird_data/Selasphorus_calliope.RData") # will come in as ebrd2.c, FAL named previously

# #merge locations data on POLYFID so it includes the center of each hex cell (LONGITUDE.y, LATITUDE.y)
  dat_merged = merge(ebrd2.c, locs, by.x = "POLYFID", by.y = "POLYFID")
  
  #now merge with the third data file for effort 
  #where count.x is number of target species and count.y is total number of eBird records (including those without the target species)
  dat_effort = merge(dat_merged, eft.c, by.x = c("POLYFID", "YEAR", "DAY"), by.y = c("POLYFID","YEAR",  "DAY")) 
  dat_effort$DAY <- as.numeric(dat_effort$DAY) 
  dat_effort$species <- "Selasphorus calliope"
  saveRDS(dat_effort, file = "data/dat_effort_cahu.rds")
```

For *S. platycercus*
```{r}
load("data/raw_eBird_data/Selasphorus_platycercus.Rdata") # will come in as ebrd2.c, FAL named previously

# #merge locations data on POLYFID so it includes the center of each hex cell (LONGITUDE.y, LATITUDE.y)
  dat_merged = merge(ebrd2.c, locs, by.x = "POLYFID", by.y = "POLYFID")
  
  #now merge with the third data file for effort 
  #where count.x is number of target species and count.y is total number of eBird records (including those without the target species)
  dat_effort = merge(dat_merged, eft.c, by.x = c("POLYFID", "YEAR", "DAY"), by.y = c("POLYFID","YEAR",  "DAY")) 
  dat_effort$DAY <- as.numeric(dat_effort$DAY) 
  dat_effort$species <- "Selasphorus platycercus"
  saveRDS(dat_effort, file = "data/dat_effort_bthu.rds")
```


For *S. rufus*
```{r}
load("data/raw_eBird_data/Selasphorus_rufus.Rdata") # will come in as ebrd2.c, FAL named previously

# #merge locations data on POLYFID so it includes the center of each hex cell (LONGITUDE.y, LATITUDE.y)
  dat_merged = merge(ebrd2.c, locs, by.x = "POLYFID", by.y = "POLYFID")
  
  #now merge with the third data file for effort 
  #where count.x is number of target species and count.y is total number of eBird records (including those without the target species)
  dat_effort = merge(dat_merged, eft.c, by.x = c("POLYFID", "YEAR", "DAY"), by.y = c("POLYFID","YEAR",  "DAY")) 
  dat_effort$DAY <- as.numeric(dat_effort$DAY) 
  dat_effort$species <- "Selasphorus rufus"
  saveRDS(dat_effort, file = "data/dat_effort_ruhu.rds")
```

